---
title: "Assignment3"
---

### 3.Use the TEDS2016 dataset to run a multiple regression model

```{r}
# Load necessary packages
library(haven)
library(dplyr)
```

```{r}
library(ggplot2)

# Read the TEDS2016 dataset
TEDS_2016 <- read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")

summary(TEDS_2016)
```

### 4,Write a function called regplot to plot a regression line

```{r}
## Creating a function: regplot 
## Combine the lm, plot and abline functions to create a regression fit plot function 
regplot=function(x,y){
  fit=lm(y~x)
  plot(x,y)
  abline(fit,col="red")
}
```

### 5.**Run a regplot on the dependent variable using: a. Age b. Education c. Income**

### 5-a. Age

```{r}
summary(lm(TEDS_2016$Age~TEDS_2016$votetsai))
```

```{r}
## Allow extra room for additional arguments/specifications
regplot=function(x,y,...){
  fit=lm(y~x)
  plot(x,y,...)
  abline(fit,col="red")
}  # "..." is called ellipsis, which is designed to take any number of named or unnamed arguments.
regplot(TEDS_2016$Age,TEDS_2016$votetsai, 
        xlab="Age",ylab="Votes for Tsai Ing-wen",col="blue",pch=20)
```

### 5-b. Education

```{r}
summary(lm(TEDS_2016$Edu~TEDS_2016$votetsai))
```

```{r}
## Allow extra room for additional arguments/specifications
regplot=function(x,y,...){
  fit=lm(y~x)
  plot(x,y,...)
  abline(fit,col="red")
}  # "..." is called ellipsis, which is designed to take any number of named or unnamed arguments.
regplot(TEDS_2016$Edu,TEDS_2016$votetsai, 
        xlab="Age",ylab="Votes for Tsai Ing-wen",col="blue",pch=20)
```

### 5-c. Income

```{r}
summary(lm(TEDS_2016$income~TEDS_2016$votetsai))
```

```{r}
## Allow extra room for additional arguments/specifications
regplot=function(x,y,...){
  fit=lm(y~x)
  plot(x,y,...)
  abline(fit,col="red")
}  # "..." is called ellipsis, which is designed to take any number of named or unnamed arguments.
regplot(TEDS_2016$income,TEDS_2016$votetsai, 
        xlab="Age",ylab="Votes for Tsai Ing-wen",col="blue",pch=20)
```

### 6. What is the problem? Why?

-   When th dependent variable is a categorical variable in a linear regression model, categorical variables are unable to indicate a linear relationship with independent variables.

-   Basically, linear regression assumes that the dependent variable is continuous and distributed normally. Categorical variables as the dependent variable result in discrete outcomes.

-   To addresss this issue, logistic regression for binary outcomes can be used with categorical dependent variables.

### 7. What can be done to improve prediction of the dependent variable?

-   The independent variables should be carefully selected and have a strong relationship with the independent variable.

-   Performance should be generalized by using complicated model and preventing overfitting.

-   Multiple models, such as Ensemble methods, can be combined to improve the strengths of each model and prediciton accuracy.
