---
title: "Assignment02"
format: html
editor: visual
---

## Assignment 02

1.  Lab01 and Lap02

2.  Review Chapters 3

```{r, warning=FALSE}
library(haven) 
library(dplyr) 
TEDS_2016 <- read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")

summary(TEDS_2016)
```

```{r}
#install.packages("descr")
TEDS_2016 <- read_stata("https://github.com/datageneration/home/blob/master/DataProgramming/data/TEDS_2016.dta?raw=true")
```

3.  what problems do you encounter when working with the dataset?
    -   To figure out missing values may be difficult

    -   Statistical analysis can be difficult because of outliers

    -   Unexpected values can indicate errors when collecting data
4.  How to deal with missing values?
    -   To remove missing values by using mean, median, and so on

    -   Multiple imputation methodologies may be helpful
5.  Explore the relationship between Tondu and other variables

```{r}
# Load necessary packages
library(ggplot2)

# Filter the data for female = 0 and female = 1
TEDS_female_0 <- TEDS_2016[TEDS_2016$female == 0, ]
TEDS_female_1 <- TEDS_2016[TEDS_2016$female == 1, ]

# Create a colorful boxplot
ggplot(TEDS_2016, aes(x = factor(female), y = Tondu, fill = factor(female))) +
  geom_boxplot() +
  scale_fill_manual(values = c("blue", "red")) +
  labs(x = "Female", y = "Tondu", title = "Boxplot of Tondu by Female") +
  theme_minimal()
```


```{r}
# Load necessary packages
library(ggplot2)

# Create a frequency table for Tondu by Female
frequency_table <- with(TEDS_2016, table(Tondu, female))

# Convert the frequency table to a data frame
frequency_df <- as.data.frame(frequency_table)

# Rename the columns for better clarity
colnames(frequency_df) <- c("Tondu", "Female", "Frequency")

# Create a colorful bar graph
ggplot(frequency_df, aes(x = Tondu, y = Frequency, fill = factor(Female))) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = c("blue", "red")) +
  labs(x = "Tondu", y = "Frequency", fill = "Female") +
  ggtitle("Frequency of Tondu by Female") +
  theme_minimal()
```


6. How about the 'votetsai' variable?
```{r}
# Load necessary packages
library(ggplot2)
library(dplyr)

# Create frequency table for votetsai variable
votetsai_freq <- table(TEDS_2016$votetsai)

# Convert frequency table to data frame
votetsai_df <- as.data.frame(votetsai_freq)
colnames(votetsai_df) <- c("Vote", "Frequency")

# Bar plot of votetsai variable
barplot(votetsai_freq, main = "Votes for Tsai Ing-wen",
        xlab = "Vote", ylab = "Frequency", col = "skyblue")
```


```{r}
# Pie chart of votetsai variable
pie(votetsai_freq, main = "Votes for Tsai Ing-wen", 
    labels = votetsai_freq, col = rainbow(length(votetsai_freq)))
```

```{r}
# Table of votetsai variable
print(votetsai_df)
```

```{r}
# Bar graph of votetsai variable with ggplot2
ggplot(votetsai_df, aes(x = Vote, y = Frequency, fill = Vote)) +
  geom_bar(stat = "identity") +
  labs(x = "Vote", y = "Frequency", fill = "Vote") +
  ggtitle("Votes for Tsai Ing-wen") +
  theme_minimal()
```



